Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-02-19 chapters/analysis_techniques.tex
Changes 1. Fixed more literature references

The first domain size metric used is the domain size derived from the spherically averaged first moment of the structure 
factor. The spherical averaging is done by averaging the values of the structure factor at the same $\mathbf{k}$ up 
till the nyquist frequency. The spherically averaged structure factor is defined as $S(k)$ where $k$ represents the 
wave numbers obtained from the spherical averaging. Next, the first moment $\langle k_1 \rangle$ is calculated as 
$\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$. Finally, the domain size is calculated as 
$L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. This domain size is used in past literature 
\textcolor{blue}{https://doi.org/10.1017/S0022112001004682, https://www.doi.org/10.1103/PhysRevE.67.046304} 
to calculate the correct scaling regime of a system undergoing spinodal decomposition.

@@

\textcolor{blue}{https://joss.theoj.org/papers/10.21105/joss.05358, https://doi.org/10.1016/j.softx.2019.100277, https://joss.theoj.org/papers/10.21105/joss.01296}

Before using taufactor, the microstructure is first binarized. This is done by first calculating the order parameter of 
the system with $\phi = \rho_b - \rho_r$ where $\phi$ is the order parameter and $\rho_b, \rho_r$ are the densities of 
the blue and red fluid respectively. Next, the interface described with $\phi$ is smoothened using the algorithm detailed 
in section \ref{section:filling_routine}. \texttt{taufactor} determines the tortuosity by comparison
of steady-state diffusive flow through a porous medium with the bulk
diffusive flow in a control volume of the same size, molecular
diffusivity, and driving force \cite{cooper_taufactor_2016}. We used
the \texttt{PeriodicSolver} to employ periodic boundary conditions. In many of the bijels synthesized using small molecule liquids, monomer is 
introduced into the oil phase and polymerized. Therefore, to perform the binarization step, we select all points where 
$\phi \leq 0$ and set their value to $0$, and all other values are set to $1$. To taufactor, $1$ represents void spaces 
and 0's are solid. \cite{cooper_taufactor_2016}

@@

The orientation of the particle is obtained from the output files from the simulation. The interface normal needs to 
be calculated from $\phi$. This is done by taking $\phi$ as calaculated from the red and blue fluid densities, then 
performing the particle fill routine described in section \ref{section:filling_routine}. Next, a mesh corresponding 
to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice 
units, which corresponds to the thickness of the interface. \textcolor{blue}{https://doi.org/10.7717/peerj.453} The 
position of the particle and its closest vertex is calculated. If this distance is larger than the first minimum in 
the radial distribution function, it is considered to be not on the interface and the next step is not performed. The 
vertex and corresponding normal closest to the position of a particle is used in the dot product, 
$\cos{\psi} = \frac{n_{int} \cdot o_{i}}{|n_{int}| |o_i|}$ where $n_{int}$ is the normal of the interface and $o_i$ 
is the orientation of particle i. After looping through all the particles, the average of $\psi$ and the number of 
particles in the interface is calculated.

@@

\subsection{Shear banding}
\label{section:yield_stress}

>>>>

The first domain size metric used is the domain size derived from the spherically averaged first moment of the structure 
factor. The spherical averaging is done by averaging the values of the structure factor at the same $\mathbf{k}$ up 
till the nyquist frequency. The spherically averaged structure factor is defined as $S(k)$ where $k$ represents the 
wave numbers obtained from the spherical averaging. Next, the first moment $\langle k_1 \rangle$ is calculated as 
$\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$. Finally, the domain size is calculated as 
$L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. \cite{kendon_inertial_2001,kendon_3d_1999} This domain size is used in past literature 
to calculate the correct scaling regime of a system undergoing spinodal decomposition.

@@

% \textcolor{blue}{https://joss.theoj.org/papers/10.21105/joss.05358, https://doi.org/10.1016/j.softx.2019.100277, https://joss.theoj.org/papers/10.21105/joss.01296}

Before using taufactor, the microstructure is first binarized. This is done by first calculating the order parameter of 
the system with $\phi = \rho_b - \rho_r$ where $\phi$ is the order parameter and $\rho_b, \rho_r$ are the densities of 
the blue and red fluid respectively. Next, the interface described with $\phi$ is smoothened using the algorithm detailed 
in section \ref{section:filling_routine}. \texttt{taufactor} determines the tortuosity by comparison
of steady-state diffusive flow through a porous medium with the bulk
diffusive flow in a control volume of the same size, molecular
diffusivity, and driving force \cite{cooper_taufactor_2016, kench_taufactor_2023}. We used
the \texttt{PeriodicSolver} to employ periodic boundary conditions. In many of the bijels synthesized using small molecule liquids, monomer is 
introduced into the oil phase and polymerized. Therefore, to perform the binarization step, we select all points where 
$\phi \leq 0$ and set their value to $0$, and all other values are set to $1$. To taufactor, $1$ represents void spaces 
and 0's are solid. \cite{cooper_taufactor_2016, kench_taufactor_2023}

@@

The orientation of the particle is obtained from the output files from the simulation. The interface normal needs to 
be calculated from $\phi$. This is done by taking $\phi$ as calaculated from the red and blue fluid densities, then 
performing the particle fill routine described in section \ref{section:filling_routine}. Next, a mesh corresponding 
to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice 
units, which corresponds to the thickness of the interface. \cite{van_der_walt_scikit-image:_2014} The 
position of the particle and its closest vertex is calculated. If this distance is larger than the first minimum in 
the radial distribution function, it is considered to be not on the interface and the next step is not performed. The 
vertex and corresponding normal closest to the position of a particle is used in the dot product, 
$\cos{\psi} = \frac{n_{int} \cdot o_{i}}{|n_{int}| |o_i|}$ where $n_{int}$ is the normal of the interface and $o_i$ 
is the orientation of particle i. After looping through all the particles, the average of $\psi$ and the number of 
particles in the interface is calculated.

@@

\subsection{Shear banding}
\label{section:shear_banding}

### 2025-02-19 chapters/lit_review.tex
Changes 1. Fixed more literature references

The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. 
\textcolor{blue}{10.1098/rspl.1903.0034, http://pubs.rsc.org/en/content/articlelanding/1907/ct/ct9079102001} Unlike surfactants, 
particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ 
is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle 
of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
is so great that thermal fluctuations at the interface can be considered to have no effect. \textcolor{blue}{https://doi.org/10.1063/1.3618553}

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. \
textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} 
Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
\textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X}

@@

In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary 
depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be 
synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} 
These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
\textcolor{blue}{https://onlinelibrary.wiley.com/doi/10.1002/smll.201600877}

@@

When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, 
as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales 
from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological 
studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} It has also been shown that particle shape changes how and when jamming occurs. 
Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
\textcolor{blue}{https://doi.org/10.1039/C3MH00047H, https://pubs.acs.org/doi/10.1021/la402436w}

@@

The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach 
and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. 
\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating 
relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
flows and implementation of fluctuating hydrodynamics in the LBM. 
\textcolor{blue}{https://pubs.acs.org/doi/10.1021/acsomega.3c06663, https://iopscience.iop.org/article/10.1209/epl/i2004-10542-5, https://link.aps.org/doi/10.1103/PhysRevE.82.056714}

@@

The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
used for soft matter flows.

\textcolor{blue}{https://pure.tue.nl/ws/files/25832941/1404.7523.pdf}

>>>>

The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907} 
Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ 
is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle 
of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
is so great that thermal fluctuations at the interface can be considered to have no effect. \cite{cheung_molecular_2011}

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. 
\cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}
Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
\cite{kaczerewska_environmental_2020, lechuga_acute_2016}

@@

In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary 
depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be 
synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} 
These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
\cite{wu_recent_2016}

@@

When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, 
as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales 
from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological 
studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} It has also been shown that particle shape changes how and when jamming occurs. 
Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
\cite{imperiali_simple_2014, sun_assembly_2013}

@@

The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach 
and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. 
\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating 
relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005}

@@

The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
used for soft matter flows. \cite{liu_multiphase_2016}

### 2025-02-19 chapters/model_params.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Fixed more literature references

\section{Simulation setup}

@@

\section{Model results}

\subsubsection{Surface tension}

In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
surface tension of the system. 
\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} 
Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
system by increasing its size. For spherical droplets, the equation simplifies to 
$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
of the interface and $R_d$ is the radius of the droplet.

@@

\subsubsection{Contact angle}

>>>>

\section{Simulation setup}
\label{section:sim_setup}

% The dynamics of the binary fluid mixture is governed by inertial,
% viscous, and surface tension forces. The relative magnitudes of these
% forces at a characteristic length scale \(L\) and characteristic
% velocity \(U\) are captured by the capillary number $\mathrm{Ca}=\frac{\eta U}{\sigma}$ and the Weber number
% \(\mathrm{We}=\frac{\rho U^2 L}{\sigma}\). Here we are primarily interested in spinodal decomposition of the mixture, 
% where we analyze the dynamics after the initial formation of the interfaces and neglect residual diffusion. Hence the 
% Peclet number \(\mathrm{Pe}=\frac{UL}{\Gamma}\) is of lesser importance and we do not consider it when choosing our 
% simulation parameters.

% The equations of motion of our model comprise the relevant materials
% properties: the density \(\rho\), viscosity \(\nu\), and surface tension \(\sigma\) of the binary fluid, and the mass \(m_p\), size \(R_p\) and aspect ratio \(\alpha\), and dipole moment \(m\) of the particles. In addition, we can control the particle volume fraction \(\phi_p\) and
% magnetic field strength \(B\). These nine quantities involve four unit
% dimensions (mass, length, time, and charge), hence we can use five
% dimensionless variables to specify the parameters of the system. These
% are the particle aspect ratio $\alpha$, particle volume fraction
% \(\phi_p\), particle vs.~fluid density ratio
% $\xi = \frac{3m_p}{4\pi \rho V_p}$, nominal Weber number $\mathrm{We} = \frac{\rho \sigma V_p^{1/3}}{\eta^2}$, and magnetic Bond
% number \(\bar{B} = m B/(\sigma A_p)\), where
% \(V_p=(4/3)\pi R_\parallel^3/\alpha^2\) is the particle volume and
% \(A_p=\max\left( \pi R_\parallel^2/\alpha, \pi R_\parallel^2/\alpha^2 \right)\)
% the area of the larger cross-section of the ellpsoidal particles.

% For our simulations, we choose units \(\Delta x\), \(\Delta t\),
% \(\Delta m\), and \(\Delta i\) such that \(V_p=\hat{V}_p(\Delta x)^3\),
% \(\nu=\hat{\nu}(\Delta x)^2/\Delta t\),
% \(\sigma=\hat{\sigma}\Delta m/(\Delta t)^2\), and
% \(m=\hat{m}\Delta i(\Delta x)^2\). We used \(V_p=2000\pi/3\),
% \(\hat{\nu}=1/6\), \(\hat{\sigma}=0.0267\), \(\hat{m}=1\), and a density
% ratio \(\xi=1/\hat{\rho}\). For reference, the values of the model
% parameters are listed in table \ref{tab:parameters}. The values of
% \(\alpha\) and \(\bar{B}\) are variable and are reported
% with the results in section \ref{sec:results}.

% %\new{We note that the dynamics of the simulations are determined by
% %the dimensionless numbers, and the actual unit values $\Delta x$,
% %$\Delta t$, $\Delta m$, and $\Delta j$ are arbitrary and only become
% %meaningful when a connection to an experimental system is made (see
% %below).}

% \begin{table}
% \centering
% \caption{Summary of the parameters of the numerical model and the values used in the simulations}
% \label{tab:parameters}
% \begin{tabular}{|c|r|}
% \hline
% Parameter & Value \\
% \hline
% $L_V/\Delta x$ & 256 \\
% $\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
% $\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
% $\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
% $\tau/\Delta t$ & 1 \\
% $g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
% $\phi_f$ & 0.5 \\
% $\phi_p$ & 0.15 \\
% $n_p$ & 1200 \\
% $\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
% $V_p/(\Delta x)^3$ & $2000\pi/3$ \\
% $m/(\Delta i(\Delta x)^2)$ & 1 \\
% $d_c/\Delta x$ & 2/3 \\
% $K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
% \hline
% \end{tabular}
% \end{table}

% We performed simulations of a binary fluid using the software package
% LB3D \cite{schmieschek_lb3d_2017} that implements the lattice Boltzmann method described in section
% \ref{section:methods}. The multicomponent
% lattice Boltzmann model is solved in a cubic box of size
% \(L_V=256\Delta x\) with periodic boundary conditions. The simulation
% box is filled with equal volume fractions \(\phi_f=0.5\) of two fluids,
% initially homogeneously mixed with a density
% \(\rho=0.7\Delta m/(\Delta x)^3\). The BGK relaxation time is set to
% \(\tau=\Delta t\) and the Shan-Chen interaction strength is set to
% \(g_{kk^\star}=0.08(\Delta x)^2/(\Delta m(\Delta t)^2)\). We performed
% preliminary simulations of a spherical droplet with these parameters and
% fitted the pressure difference inside and outside the droplet to the
% Young-Laplace law, which yielded a surface tension
% \(\sigma=0.0267\Delta m/(\Delta t)^2\). To study the influence of
% anisotropic particle shapes on the bijel formation, we performed
% simulations for particles with three different aspect ratios:
% \(\alpha=1\) for spherical particles, \(\alpha=2\) for prolate
% ellipsoids, and \(\alpha=1/2\) for oblate ellipsoids. To match the
% particle volume fraction \(\phi_p\) between the different particle
% shapes, we kept the volume of the particles fixed and used the same
% number of particles for each aspect ratio. The radius along the symmetry
% axis of the particles was calculated from
% \(V_p=(4/3)\pi R_\parallel^3/\alpha^2\), yielding
% \(R_\parallel=7.9\Delta x\) for spheres, \(R_\parallel=12.6\Delta x\)
% for prolate ellipsoids, and \(R_\parallel=5\Delta x\) for oblate
% ellipsoids, respectively. Particles were added to the fluid by placing
% them randomly inside the box. The lubrication cutoff distance was set to
% the value \(d_c=(2/3)\Delta x\) recommended by Ladd
% \cite{ladd_lattice-boltzmann_2001}, and the strength of the Hertz
% potential was set to \(K_H=100\Delta m/((\Delta x)^{1/2}(\Delta t)^2)\).
% We first equilibrated the particle positions and orientations by
% evolving only the equations of motion of the particles, while the fluid
% remained in its initial configuration, until the minimum particle
% distance exceeded \(1.2\cdot\max(R_\parallel,R_\parallel/\alpha)\).
% After the equilibration, the magnetic flux density
% \(\vec{B}=B\hat{\vec{z}}\) was switched on and the full system was
% evolved for \(10^5\) timesteps. In the course of the simulation, the binary mixture undergoes spinodal decomposition. 
% The particles adsorb at the coarsening interface and eventually become jammed, resulting in the bicontinuous phase 
% morphology of the bijel.

% It is worth discussing briefly the possible realization of our model in
% experiments. A common choice for bijel formation in binary liquids is a
% mixture of water and lutidine
% \cite{clegg_emulsification_2007,herzig_bicontinuous_2007}. The surface
% tension between the phases of a water-lutidine system at
% \(40^\circ\mathrm{C}\) is around \(\sigma=0.22\ \mathrm{mN/m}\) and the
% dynamic viscosity of the lutidine-rich phase is around
% \(\eta=2.38\ \mathrm{mPa\,s}\) \cite{grattoni_lower_1993}. Ellipsoidal
% particles with various aspect ratios can be formed by mechanically
% stretching spherical particles \cite{trevenen_gradient_2021}. Such
% particles can be magnetically functionalized by e-beam deposition of a
% Nickel layer. Fei et
% al.~\cite{fei_magneto-capillary_2018,fei_magneto-capillary_2020}
% fabricated coated \(4\ \mathrm{\mu m}\) polystyrene particles with a
% permanent magnetic dipole moment of
% \(m\approx3\cdot10^{-14}\ \mathrm{Am^2}\). It was shown that the dipole moment is oriented in the direction parallel to the coated interface \cite{yan_linking_2012,yan_rotating_2014}, i.e., it can be aligned with the axis of ellipsoidal particles.
% For the given surface tension, the capillary torque on a particle adsorbed at an interface is approximately
% $8.8\cdot10^{-16}\ \mathrm{Nm}$. We thus can estimate that a magnetic
% flux density of \(30\ \mathrm{mT}\) is able to exert a magnetic torque
% that exceeds the capillary torque.
% We note that under these conditions,
% the dipole-dipole interaction is on the order of
% \(10^{-16}\ \mathrm{J}\) and an order of magnitude smaller than the
% particle-interface interaction which is of order
% \(10^{-15}\ \mathrm{J}\). %Unlike previous works
% %\cite{xie_direct_2017,xie_controllable_2021}, we therefore cannot
% %neglect the magnetic dipole-dipole interactions between particles.For these bijel properties and the parameters given in
% table \ref{tab:parameters}, the spatial resolution of our
% simulations is $\Delta x\approx252\ \mathrm{nm}$, and the time step
% is $\Delta t=624\ \mathrm{ns}$. This corresponds to a system side length of $L_V \approx 64.5\ \mathrm{\mu m}$ and a runtime of
% $T \approx 62.4\ \mathrm{ms}$.

@@

\section{Model results}
\label{section:model_results}

\subsection{Surface tension}
\label{section:model_surface_tension}

In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
surface tension of the system. \cite{sun_assembly_2013, berry_measurement_2015}
Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
system by increasing its size. For spherical droplets, the equation simplifies to 
$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
of the interface and $R_d$ is the radius of the droplet.

@@

\subsection{Contact angle}
\label{section:model_contact_angle}
